{\it E}nKCF: Ensemble of Kernelized Correlation Filters for Object Tracking in High Speed

### 2017-04-28 draft.tex
Results Section Finished other than Re-detection

We compare the proposed tracker to other state-of-the-art high speed trackers using the \textit{Precision} and \textit{Success\:Rate} metrics. Precision is computed by thresholding the average euclidean distance between the ground truth and tracking output over the frames of one sequence. In precision, we rank the trackers based on the precision numbers at 20 pixels. The success rate metric evaluates the overlap between the ground truth and tracking output. The intersection-to-union ratio of two regions over the frames of one sequence. Finally, we count the number of frames with overlap larger than the success rate threshold and divide it by the number of frames. We compare our tracker to some other high-speed ($\geq$300 fps) state-of-the-art trackers including KCF\cite{henriques2015high}, CSK \cite{henriques2012exploiting}, STC\cite{zhang2014fast}, MOSSE\cite{bolme2010visual,henriques2015high}. Also, some relatively lower-speed ($\geq$50) trackers are used to evaluate the robustness of the proposed trackers. These trackers include SAMF\cite{li2014scale}, DSST\cite{danelljan2014accurate}, LCT\cite{ma2015long}, MEEM\cite{zhang2014meem} and Struck\cite{hare2012efficient}.
Fig.~\ref{fig:UAV123_DATASET} shows the results on the UAV123 dataset.

@@

>>>>

\textbf{Hyperparameter Selections.} Tuning the hyper-parameters of the committee of the correlation filters are important as the each correlation filter addresses the weakness of another one. For instance, $R_{t}^{L}$'s main task is to recover from the previous frame where only $R_{s}$ and particle filter's prior distribution are used to estimate scale and translation. We set the learning rates ($\beta$) of $R_{t}^{L}$, $R_{t}^{S}$, and $R_{s}$ as $0.020$, $0.020$ and $0.010$. The desired response and hanning window for each KCF is shown in fig.~\ref{fig:Filters}. Finally, the Gaussian kernel parameter, $\alpha$ is tuned to $0.6$, $0.4$, and $0.4$ for $R_{t}^{L}$, $R_{t}^{S}$, and $R_{s}$. In our particle filter implementation, we employ $1000$ particles and use the \textit{efficient number of samples} metric shown below to determine whether we need to perform importance re-sampling or not to keep reasonable variance.
\begin{equation}
  \hat{N}_{eff} = \dfrac{1}{\sum_{i=1}^{P}(w_{p})^{2}}, 
\end{equation}
 where $w$ represents the particles' weights and re-sampling is performed only if $\hat{N}_{eff}$ is smaller than three.

\textbf{Features Selections.} We use the fast Histogram of Oriented Gradients (fHoG)\cite{felzenszwalb2010object} and Color-naming\cite{van2009learning} features to learn target and background models. $R_{t}^{L}$ uses both fHoG and color features as it covers a large ROI where fHoG features may not be reliable alone. On the other hand, $R_{t}^{S}$ is assigned only fHoG features as it covers smaller ROI. Finally, $R_{s}$ uses both fHoG and color features as it is assigned lower template size, yielding space to exploit two feature modalities.

@@

\textbf{Overall Performance without Re-detection on UAV123 Dataset.} We compare the proposed tracker to other state-of-the-art high speed trackers using the \textit{Precision} and \textit{Success\:Rate} metrics. Precision is computed by thresholding the average euclidean distance between the ground truth and tracking output over the frames of one sequence. In precision, we rank the trackers based on the precision numbers at 20 pixels. The success rate metric evaluates the overlap between the ground truth and tracking output. The intersection-to-union ratio of two regions over the frames of one sequence. Finally, we count the number of frames with overlap larger than the success rate threshold and divide it by the number of frames. We compare our tracker to some other high-speed ($\geq$300 fps) state-of-the-art trackers including KCF\cite{henriques2015high}, CSK \cite{henriques2012exploiting}, STC\cite{zhang2014fast}, MOSSE\cite{bolme2010visual,henriques2015high}. Also, some relatively lower-speed ($\geq$50) trackers are used to evaluate the robustness of the proposed trackers. These trackers include SAMF\cite{li2014scale}, DSST\cite{danelljan2014accurate}, LCT\cite{ma2015long}, MEEM\cite{zhang2014meem} and Struck\cite{hare2012efficient}.
Fig.~\ref{fig:UAV123_DATASET} shows the results on the UAV123 dataset. The E$n$KCF tracker outperforms the other methods in high-speed trackers category by $3\%$-$15\%$ at 20 pixels precision accuracy whereas it is only $5\%$ worse than SAMF, DSST and Struck on the same dataset although it is $10$-$20$ times faster than these trackers. On the other hand, the E$n$KCF does a decent job on approximating the scale of the target in highly efficient manner. This is proved by the fact that it ranks third best tracker in terms of \textit{area under curve} (AUC) value for the success rate plot. It outperforms the high speed trackers by about $20\%$-$25\%$ in AUC metric. Interestingly, it performs even better than most of the low speed trackers. For instance, it outperforms Struct and DSST by $5\%$ and $10\%$ while running at more than $30$ and $10$ times larger operation rate.

\textbf{Overall Performance without Re-detection on OTB100 Dataset.} In addition to UAV123 dataset, we test the E$n$KCF tracker on the OTB100 dataset to evaluate how good it generalizes to a traditional object tracking dataset. Again, it performs slightly better than the high speed trackers in precision. Interestingly, it outperforms the another correlation filter based tracker, DSST while running only $5\%$ behind of another low-speed scale adaptive SAMF tracker. As in UAV123 dataset, the E$n$KCF performs exceptionally in handling the scale changes. It is ranked as the fifth best tracker while being the second highest speed tracker behind MOSSE. It performs only around $2\%$ worse than SAMF and MEEM trackers in terms of AUC. These numbers prove that E$n$KCF is not only a good candidate for tracking on a UAV-based mobile platform but also mobile platforms on smart phones.
